---
title: "5052_Presentation_CPXYY"
author: "Yingtong Zhou"
date: "4/30/2020"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, cache=TRUE}
setwd("~/Desktop/QMSS - CU/Spring 2020/GR5052_Practicum")
library(ggplot2)
library(dplyr)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(tidytext)
library(tidyverse)
library(plotrix)
library(quanteda)

loan <- read.csv("~/Desktop/QMSS - CU/Spring 2020/GR5052_Practicum/df_loan_sample.csv", 
                       comment.char="#", stringsAsFactors = FALSE)
```


# Bar Charts - Sub Issue vs. # of Complaints
```{r, message=FALSE, warning=FALSE, cache=TRUE}
unique(loan$Sub_issue)

si_bar <- loan %>% 
  group_by(Sub_issue) %>% 
  summarize(cnt = n()) %>% 
  arrange(desc(cnt))

gg_si <- ggplot(si_bar, aes(x = reorder(Sub_issue, -cnt), y = cnt)) +
  geom_bar(stat = "identity", fill = "lightskyblue1") +
  theme(axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size = 10, angle = 70)) +
  geom_text(aes(label = cnt), 
            hjust = 0.75, 
            vjust = 0.5) +
  coord_flip() +
  ylim(0, 10000) + 
  xlab(NULL)
  

gg_si
```


# Table - Company_public_response vs. # of Complaints
```{r, message=FALSE, warning=FALSE, cache=TRUE}
cpr_bar <- loan %>% 
  group_by(Company_public_response) %>% 
  summarize(cnt = n()) %>% 
  arrange(desc(cnt))

cpr_bar$Company_public_response[cpr_bar$Company_public_response == ""] <- "NA"

cpr_bar
```


# Bar Charts - Company_public_response vs. # of Complaints
```{r, message=FALSE, warning=FALSE, cache=TRUE}
si_cpr_bar <- loan %>% 
  mutate(npr = ifelse(grepl("CFPB", Company_public_response),
                      "Yes",
                      "No")) %>%
  group_by(Sub_issue, npr) %>%
  summarize(cnt = n()) %>% 
  arrange(desc(cnt))

gg_si_cpr <- ggplot(si_cpr_bar, aes(x = reorder(Sub_issue, -cnt), y = cnt, fill = npr)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  ylim(0, 10000) + 
  xlab(NULL) +
  ylab(NULL) +
  ggtitle("Company has responded to the consumer\nand the CFPBand chooses not to\nprovide a public response")

gg_si_cpr
```


# Bar Charts - Company_response_to_consumer & Sub_issue vs. # of Complaints
```{r, message=FALSE, warning=FALSE, cache=TRUE}
si_crc_bar <- loan %>% 
  group_by(Sub_issue, Company_response_to_consumer) %>% 
  summarize(cnt = n()) %>% 
  arrange(desc(cnt))

si_crc_bar$Company_response_to_consumer[si_crc_bar$Company_response_to_consumer == ""] <- "NA"

gg_si_crc <- ggplot(si_crc_bar, aes(x = reorder(Sub_issue, -cnt), y = cnt, fill = Company_response_to_consumer)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  ylim(0, 10000) + 
  xlab(NULL) +
  ylab(NULL)
  

gg_si_crc
```


# Bar Charts - Tags & Sub_issue vs. # of Complaints
```{r, message=FALSE, warning=FALSE, cache=TRUE}
si_t_bar <- loan %>% 
  group_by(Sub_issue, Tags) %>% 
  summarize(cnt = n()) %>% 
  arrange(desc(cnt))

si_t_bar$Tags[si_t_bar$Tags == ""] <- "None"

gg_si_t <- ggplot(si_t_bar, aes(x = reorder(Sub_issue, -cnt), y = cnt, fill = Tags)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  xlab(NULL) +
  ylab(NULL)
  

gg_si_t
```


# Sub Issue vs. Timely Response
```{r, message=FALSE, warning=FALSE, cache=TRUE}
com_tut <- loan %>% 
  filter(!Timely_response_ == "") %>% 
  group_by(Sub_issue, Timely_response_) %>% 
  summarize(cnt1 = n())

gg_tut <- ggplot(com_tut, aes(x = reorder(Sub_issue, -cnt1), y = cnt1, fill = Timely_response_)) +
  geom_bar(stat = "identity",position = "dodge") +
  geom_text(aes(label = cnt1), 
            hjust = 0.05, 
            vjust = 0.5,
            position = position_dodge(width = 1),
            size = 3) +
  coord_flip() +
  ylim(0, 10000) +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 9)) +
  xlab(NULL)

gg_tut
```


# Untimely%
```{r, message=FALSE, warning=FALSE, cache=TRUE}
com_ut <- left_join(com_tut, si_bar, by = "Sub_issue") %>% 
  mutate(ptn = round(cnt1 / cnt, 3))

gg_prop <- ggplot(com_ut, aes(x = reorder(Sub_issue, -cnt),
                              y = ptn, fill = Timely_response_)) +
  geom_bar(stat = "identity",position = "dodge") +
  geom_text(aes(label = ptn), 
            hjust = 0.25, 
            vjust = 0.5,
            position = position_dodge(width = 1),
            size = 3) +
  coord_flip() +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 9)) +
  xlab(NULL) +
  ylab("Proportion")

gg_prop
```


# Bar Charts -  Company_response_to_consumer vs. # of Complaints
```{r, message=FALSE, warning=FALSE, cache=TRUE}
crc_bar <- loan %>% 
  group_by(Company_response_to_consumer) %>% 
  summarize(cnt = n()) %>% 
  arrange(desc(cnt))

gg_crc <- ggplot(crc_bar, aes(x = reorder(Company_response_to_consumer, -cnt), y = cnt)) +
  geom_bar(stat = "identity", fill = "lightskyblue1") +
  theme(axis.text.y = element_text(size = 10),
         axis.text.x = element_text(size = 10)) +
  geom_text(aes(label = cnt), 
            hjust = 0.75, 
            vjust = 0.5) +
  coord_flip() +
  ylim(0, 20000) + 
  xlab(NULL)
  

gg_crc
```


# Text Analysis
# Narratives Comparison of Timely & Untimely
## Generate Corpus
```{r, message=FALSE, warning=FALSE, cache=TRUE}
timely_df <- loan %>% 
  filter(Timely_response_ == "Yes") %>% 
  select(Consumer_complaint_narrative) %>% 
  slice(1:500)

timely_corpus <- Corpus(VectorSource(timely_df))

untimely_df <- loan %>% 
  filter(Timely_response_ == "No") %>% 
  select(Consumer_complaint_narrative)

untimely_corpus <- Corpus(VectorSource(untimely_df))
```


# Clean Narratives
```{r, message=FALSE, warning=FALSE, cache=TRUE}
removeNumPunct <- function(x){gsub("[^[:alpha:][:space:]]*", "", x)}

clean_corpus <- function(corpus){
  corpus <- tm_map(corpus, removeWords, c("XXXX", "XX"))
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "xxxx"))
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, content_transformer(removeNumPunct))
  corpus <- tm_map(corpus, stripWhitespace)
  return(corpus)
}

timely_clean <- clean_corpus(timely_corpus)
untimely_clean <- clean_corpus(untimely_corpus)

timely_stem <- tm_map(timely_clean, stemDocument)
untimely_stem <- tm_map(untimely_clean, stemDocument)

stemCompletion2 <- function(x, dictionary) {
   x <- unlist(strsplit(as.character(x), " "))
   x <- x[x != ""]
   x <- stemCompletion(x, dictionary=dictionary)
   x <- paste(x, sep="", collapse=" ")
   PlainTextDocument(stripWhitespace(x))
}

timely_comp <- lapply(timely_stem, stemCompletion2, dictionary = timely_clean)
untimely_comp <- lapply(untimely_stem, stemCompletion2, dictionary = untimely_clean)

timely_comp <- as.VCorpus(timely_comp)
untimely_comp <- as.VCorpus(untimely_comp)

# Create DTM
timely_dtm <- DocumentTermMatrix(timely_comp)
untimely_dtm <- DocumentTermMatrix(untimely_comp)
```


## Timely Word Cloud
```{r, message=FALSE, warning=FALSE, cache=TRUE}
m <- as.matrix(timely_dtm)
v <- sort(colSums(m),decreasing = TRUE)
d <- data.frame(word = names(v),freq = v)

set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 25,
          max.words = 200, random.order = FALSE, rot.per = 0.35, 
          colors = brewer.pal(8, "Dark2"))
```


## Untimely Word Cloud
```{r, message=FALSE, warning=FALSE, cache=TRUE}
m2 <- as.matrix(untimely_dtm)
v2 <- sort(colSums(m2),decreasing = TRUE)
d2 <- data.frame(word = names(v2),freq = v2)

set.seed(1234)
wordcloud(words = d2$word, freq = d2$freq, min.freq = 25,
          max.words = 200, random.order = FALSE, rot.per = 0.35, 
          colors = brewer.pal(8, "Dark2"))
```


## Common Words
```{r, message=FALSE, warning=FALSE, cache=TRUE}
timely_word <- d[10:40, ]
untimely_word <- d2 %>% 
  filter(word %in% timely_word$word) %>% 
  rename(untimely_cnt = freq)

common_word <- left_join(untimely_word, timely_word)
(common_word <- common_word[1:20, ])

plot_cw <- pyramid.plot(common_word$freq, common_word$untimely_cnt,
                       labels = common_word$word, gap = 10, 
                       top.labels = c("Timely", " ", "Untimely"),
                       main = "Words in Common", laxlab = NULL, 
                       raxlab = NULL, unit = NULL, labelcex = 0.5)
```


## Common Words - from each group
```{r, message=FALSE, warning=FALSE, cache=TRUE}
timely_word <- d[10:25, ]
untimely_word <- d2[10:25, ]

timely_word_new <- distinct(rbind(timely_word, d %>% filter(word %in% untimely_word$word)))
untimely_word_new <- distinct(rbind(untimely_word, d2 %>% filter(word %in% timely_word$word))) %>% 
  rename(ut_freq = freq)

common_word_new <- full_join(timely_word_new, untimely_word_new, by = "word") %>% 
  na.omit()

common_word_new

plot_cw2 <- pyramid.plot(common_word_new$freq, common_word_new$ut_freq,
                       labels = common_word_new$word, gap = 10, 
                       top.labels = c("Timely", " ", "Untimely"),
                       main = "Words in Common", laxlab = NULL, 
                       raxlab = NULL, unit = NULL, labelcex = 0.5)
```


# Simplicity - little difference
```{r, message=FALSE, warning=FALSE, cache=TRUE}
timely_rbt <- textstat_readability(as.character(timely_df),
                     measure=c('Flesch','Flesch.Kincaid',
                  'meanSentenceLength','meanWordSyllables'))

untimely_rbt <- textstat_readability(as.character(untimely_df),
                     measure=c('Flesch','Flesch.Kincaid',
                  'meanSentenceLength','meanWordSyllables'))
rbt <- rbind(timely_rbt, untimely_rbt)
rbt[1, 1] <- "Timely"
rbt[2, 1] <- "Untimely"

rbt
```




# Narratives Comparison of Company_response_to_consumer
## Generate Corpus
```{r, message=FALSE, warning=FALSE, cache=TRUE}
cnmr_df <- loan %>% 
  filter(Company_response_to_consumer == "Closed with non-monetary relief") %>% 
  select(Consumer_complaint_narrative) %>% 
  slice(1:500)

cnmr_corpus <- Corpus(VectorSource(cnmr_df))

ce_df <- loan %>% 
  filter(Company_response_to_consumer == "Closed with explanation") %>% 
  select(Consumer_complaint_narrative) %>% 
  slice(1:500)

ce_corpus <- Corpus(VectorSource(ce_df))

cmr_df <- loan %>% 
  filter(Company_response_to_consumer == "Closed with monetary relief") %>% 
  select(Consumer_complaint_narrative)

cmr_corpus <- Corpus(VectorSource(cmr_df))

ur_df <- loan %>% 
  filter(Company_response_to_consumer == "Untimely response") %>% 
  select(Consumer_complaint_narrative)

ur_corpus <- Corpus(VectorSource(ur_df))
```


# Clean Narratives
```{r, message=FALSE, warning=FALSE, cache=TRUE}
cnmr_clean <- clean_corpus(cnmr_corpus)
ce_clean <- clean_corpus(ce_corpus)
cmr_clean <- clean_corpus(cmr_corpus)
ur_clean <- clean_corpus(ur_corpus)

cnmr_stem <- tm_map(cnmr_clean, stemDocument)
ce_stem <- tm_map(ce_clean, stemDocument)
cmr_stem <- tm_map(cmr_clean, stemDocument)
ur_stem <- tm_map(ur_clean, stemDocument)

cnmr_comp <- lapply(cnmr_stem, stemCompletion2, dictionary = cnmr_clean)
ce_comp <- lapply(ce_stem, stemCompletion2, dictionary = ce_clean)
cmr_comp <- lapply(cmr_stem, stemCompletion2, dictionary = cmr_clean)
ur_comp <- lapply(ur_stem, stemCompletion2, dictionary = ur_clean)

cnmr_comp <- as.VCorpus(cnmr_comp)
ce_comp <- as.VCorpus(ce_comp)
cmr_comp <- as.VCorpus(cmr_comp)
ur_comp <- as.VCorpus(ur_comp)

# Create DTM
cnmr_dtm <- DocumentTermMatrix(cnmr_comp)
ce_dtm <- DocumentTermMatrix(ce_comp)
cmr_dtm <- DocumentTermMatrix(cmr_comp)
ur_dtm <- DocumentTermMatrix(ur_comp)
```


## Closed with non-monetary relief Word Cloud
```{r, message=FALSE, warning=FALSE, cache=TRUE}
ma <- as.matrix(cnmr_dtm)
va <- sort(colSums(ma),decreasing = TRUE)
da <- data.frame(word = names(va),freq = va)

set.seed(1234)
wordcloud(words = da$word, freq = da$freq, min.freq = 25,
          max.words = 200, random.order = FALSE, rot.per = 0.35, 
          colors = brewer.pal(8, "Dark2"))
```


## Closed with explanation Word Cloud
```{r, message=FALSE, warning=FALSE, cache=TRUE}
mb <- as.matrix(ce_dtm)
vb <- sort(colSums(mb),decreasing = TRUE)
db <- data.frame(word = names(vb),freq = vb)

set.seed(1234)
wordcloud(words = db$word, freq = db$freq, min.freq = 25,
          max.words = 200, random.order = FALSE, rot.per = 0.35, 
          colors = brewer.pal(8, "Dark2"))
```


## Closed with monetary relief Word Cloud
```{r, message=FALSE, warning=FALSE, cache=TRUE}
mc <- as.matrix(cmr_dtm)
vc <- sort(colSums(mc),decreasing = TRUE)
dc <- data.frame(word = names(vc),freq = vc)

set.seed(1234)
wordcloud(words = dc$word, freq = dc$freq, min.freq = 25,
          max.words = 200, random.order = FALSE, rot.per = 0.35, 
          colors = brewer.pal(8, "Dark2"))
```


## Untimely response Word Cloud
```{r, message=FALSE, warning=FALSE, cache=TRUE}
md <- as.matrix(ur_dtm)
vd <- sort(colSums(md),decreasing = TRUE)
dd <- data.frame(word = names(vd),freq = vd)

set.seed(1234)
wordcloud(words = dd$word, freq = dd$freq, min.freq = 25,
          max.words = 200, random.order = FALSE, rot.per = 0.35, 
          colors = brewer.pal(8, "Dark2"))
```


# Simplicity - Closed with monetary relief - Highest Flesch - Easiest to Read
```{r, message=FALSE, warning=FALSE, cache=TRUE}
cnmr_rbt <- textstat_readability(as.character(cnmr_df),
                     measure=c('Flesch','Flesch.Kincaid',
                  'meanSentenceLength','meanWordSyllables'))

ce_rbt <- textstat_readability(as.character(ce_df),
                     measure=c('Flesch','Flesch.Kincaid',
                  'meanSentenceLength','meanWordSyllables'))

cmr_rbt <- textstat_readability(as.character(cmr_df),
                     measure=c('Flesch','Flesch.Kincaid',
                  'meanSentenceLength','meanWordSyllables'))

ur_rbt <- textstat_readability(as.character(ur_df),
                     measure=c('Flesch','Flesch.Kincaid',
                  'meanSentenceLength','meanWordSyllables'))

rbt <- rbind(cnmr_rbt, ce_rbt, cmr_rbt, ur_rbt)

rbt[1, 1] <- "Closed with non-monetary relief"
rbt[2, 1] <- "Closed with explanation"
rbt[3, 1] <- "Closed with monetary relief"
rbt[4, 1] <- "Untimely response"

rbt
```


# Sentiment Analysis
# Negative Scores of Narratives & Company_response_to_consumer
## Highest Negative Average Score: Closed with monetary relief
```{r, message=FALSE, warning=FALSE, cache=TRUE}
Neg_Sc <- function(ctgy) {
  loan %>% 
  filter(Company_response_to_consumer == ctgy) %>% 
  mutate(RowNum = row_number()) %>% 
  unnest_tokens(word, Consumer_complaint_narrative) %>% 
  inner_join(get_sentiments("afinn")) %>% 
  select(RowNum, value) %>% 
  filter(value < 0) %>% 
  group_by(RowNum) %>% 
  mutate(Score = sum(value)) %>% 
  select(RowNum, Score) %>% 
  distinct() %>% 
  plyr::summarise(mean(Score))
}

crc_cat <- c("Closed with non-monetary relief", "Closed with explanation", "Closed with monetary relief", "Untimely response")

NS <- unlist(lapply(crc_cat, Neg_Sc))
(ns_cat <- cbind(crc_cat, NS))
```


# Positive Scores of Narratives & Company_response_to_consumer
## Highest Positive Average Score: Closed with monetary relief 
## (as well - this is a very emotional category)
```{r, message=FALSE, warning=FALSE, cache=TRUE}
Pos_Sc <- function(ctgy) {
  loan %>% 
  filter(Company_response_to_consumer == ctgy) %>% 
  mutate(RowNum = row_number()) %>% 
  unnest_tokens(word, Consumer_complaint_narrative) %>% 
  inner_join(get_sentiments("afinn")) %>% 
  select(RowNum, value) %>% 
  filter(value > 0) %>% 
  group_by(RowNum) %>% 
  mutate(Score = sum(value)) %>% 
  select(RowNum, Score) %>% 
  distinct() %>% 
  plyr::summarise(mean(Score))
}

PS <- unlist(lapply(crc_cat, Pos_Sc))
(ps_cat <- cbind(crc_cat, PS))
```